Experiment 3: ratings

### 2021-06-05 analysis/exp3_analysis.Rmd
overall R^2 on plots

```{r}
p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

@@

```{r}
p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  stat_cor(method = "pearson")

>>>>

```{r}
p1 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_likelihood, 
               label = paste(..rr.label.., sep = "~`,`~")))

p2 <- adult_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson")
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_interest, 
               label = paste(..rr.label.., sep = "~`,`~")))

@@

```{r}
p1 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_likelihood, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Likelihood") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson") 
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_likelihood, 
               label = paste(..rr.label.., sep = "~`,`~")))

p2 <- child_agg %>% ggplot(aes(x=chose_target, y=prop_target_interest, color=relation)) + geom_point() +
  xlab("Proportion of Adults Choosing Target") +
  ylab("Luce choice of Target vs. Distractor Interestingness") +
  xlim(0,1) + ylim(0,1) + theme_classic() +
  geom_abline(slope=1, intercept=0, linetype="dashed") +
  #stat_cor(method = "pearson")
  stat_cor(inherit.aes = F, aes(x=chose_target, y=prop_target_interest, 
               label = paste(..rr.label.., sep = "~`,`~")))
